---
title: "Create your R package"
author: "Ramon Gallego"
date: "5/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval= FALSE)
```

## First step

Install the following packages

```{r echo = T, eval = F}
install.packages(c('testthat', 'usethis', 'roxygen2'))
```

## Go to the dropdown option on the top-right corner of Rstudio 
Click New Project -> New Directory -> R package

Give it a name

If available, tick the box for create a git repo

Tick the Open in new session

Click in 'Create Project'


## Description

Edit the Title and description fields

## R

Add the functions in a R script

## documentation

go to the r packages  (book)[http://r-pkgs.had.co.nz/man.html]

Copy the code chunk that starts with #', and paste them on top of every function in our Temperatures.r file

Edit to your liking

run this from the console

```{r}
devtools::document()
```

THis creates the new help file

Test it
```{r}
?fahrenheit_to_celsius
```

## tests

They are really important - check values and functionalities

Run this
```{r}
usethis::use_test("temp-test")
```

It tells you what it does!! now you can edit the test itself


### THE EXPECT TOOL IS THE COOLEST



paste this code in the newly created test-temp-test.R file

```{r}
test_that("f2C works", {
  expect_equivalent(round(fahrenheit_to_celsius(0),2), -17.78)
})

test_that("f2C vectors", {
  expect_equal(fahrenheit_to_celsius(c(0,100)), c(-17.7778, 37.7778))
})

```

Save it

Now you can test if the function works

click Ctrl (or cmd in mac) + shift + T



